### 2018-11-19 Sections/economics_of_the_quantum_internet.tex
Formatting, algs

\dropcap{I}{n} Table.~\ref{tab:summary_ec_models} we summarise the economic models and parameters we developed, and applied them to several illustrative scaling functions of particular interest: linear, polynomial, and exponential.

>>>>

\dropcap{I}{n} Tab.~\ref{tab:summary_ec_models} we summarise the economic models and parameters we developed, and applied them to several illustrative scaling functions of particular interest: linear, polynomial, and exponential.

### 2018-11-19 Sections/optical_stability_in_quantum_networks.tex
Formatting, algs

In Table.~\ref{table:summary_inter} we summarise the network protocols discussed in Part.~\ref{part:protocols} in terms of the types of interference they rely upon. This creates a picture of which are more realistic from a near-term engineering perspective.

>>>>

In Tab.~\ref{table:summary_inter} we summarise the network protocols discussed in Part.~\ref{part:protocols} in terms of the types of interference they rely upon. This creates a picture of which are more realistic from a near-term engineering perspective.

### 2018-11-19 Sections/state_of_the_art.tex
More indexing
Finished indexing hierarchy
Ecosystem fig
Formatting, algs

@@

\dropcap{Q}{uantum} state teleportation has attracted broad experimental interest and been subject to widespread demonstration across many physical architectures, becoming one of the most well investigated protocols in experimental quantum information science. Table.~\ref{tab:state_tomo} summarises some of the notable developments.

@@

\dropcap{W}{ith} the development of quantum technology, QKD will gradually become more and more practical and economically accessible. Bennett, one of the proposers of the BB84 protocol, first demonstrated the protocol on an optical platform with a distance of 30cm \cite{bib:JC_5_3}. Since then, experiments have developed rapidly from indoors to outdoors, over ever-increasing distances, with commercial QKD units even available as off-the-shelf products. Table.~\ref{tab:QKD_table} summarises some major developments in the field.

@@

\dropcap{E}{ntanglement} purification has been very successful in optical systems. Table.~\ref{tab:ent_pur} lists some of the major developments.

@@

\subsection{Single-photon states} \index{Single-photon state preparation}

@@

\subsection{Quantum dots} \index{Quantum dot sources}

@@

\subsection{Superconducting rings} \index{Superconducting rings}

@@

\subsection{Optical waveguides} \index{Optical waveguides}

@@

\subsection{Superconducting rings}\index{Superconducting rings}

>>>>

\comment{Do not review this section Jon. In the process of completely reformatting.}

@@

\dropcap{Q}{uantum} state teleportation has attracted broad experimental interest and been subject to widespread demonstration across many physical architectures, becoming one of the most well investigated protocols in experimental quantum information science. Tab.~\ref{tab:state_tomo} summarises some of the notable developments.

@@

\dropcap{W}{ith} the development of quantum technology, QKD will gradually become more and more practical and economically accessible. Bennett, one of the proposers of the BB84 protocol, first demonstrated the protocol on an optical platform with a distance of 30cm \cite{bib:JC_5_3}. Since then, experiments have developed rapidly from indoors to outdoors, over ever-increasing distances, with commercial QKD units even available as off-the-shelf products. Tab.~\ref{tab:QKD_table} summarises some major developments in the field.

@@

\dropcap{E}{ntanglement} purification has been very successful in optical systems. Tab.~\ref{tab:ent_pur} lists some of the major developments.

@@

\subsection{Single-photon states} \index{Single-photons!Preparation}

@@

\subsection{Quantum dots} \index{Quantum dots!Sources}

@@

\subsection{Superconducting rings} \index{Superconductors!Rings}

@@

\subsection{Optical waveguides} \index{Optical!Waveguides}

@@

\subsection{Superconducting rings}\index{Superconductors!Rings}
